Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-11-19 manuscript/manuscript.tex
specify section in CK reference (this addresses #171)

Once we have used the ITS to choose the lag time, we can check whether a given transition probability matrix $\mathbf{P}(\tau)$ is approximately Markovian using the Chapman-Kolmogorov (CK) test~\cite{noe-folding-pathways}.
The CK property for a Markovian matrix is,
\begin{equation}
\mathbf{P}(k \tau) = \mathbf{P}^k(\tau),
\end{equation}
where the left-hand side of the equation corresponds to an MSM estimated at lag time $k\tau$, where $k$ is an integer larger than~$1$, whereas the right-hand side of the equation is our estimated MSM transition probability matrix to the $k^\textrm{th}$ power.
By assessing how well the approximated transition probability matrix adheres to the CK property, we can validate the appropriateness of the Markovian assumption for the model~\cite{msm-jhp,noe-folding-pathways}.

>>>>

Once we have used the ITS to choose the lag time, we can check whether a given transition probability matrix $\mathbf{P}(\tau)$ is approximately Markovian using the Chapman-Kolmogorov (CK) test~\cite{noe-folding-pathways,msm-jhp}.
The CK property for a Markovian matrix is,
\begin{equation}
\mathbf{P}(k \tau) = \mathbf{P}^k(\tau),
\end{equation}
where the left-hand side of the equation corresponds to an MSM estimated at lag time $k\tau$, where $k$ is an integer larger than~$1$, whereas the right-hand side of the equation is our estimated MSM transition probability matrix to the $k^\textrm{th}$ power.
By assessing how well the approximated transition probability matrix adheres to the CK property, we can validate the appropriateness of the Markovian assumption for the model (see Sec.~IV.F in~\cite{msm-jhp}).
